Understanding the Impact of Socioeconomic and Regional Factors on Health and Educational Outcomes

### 2024-12-15 paper.qmd
adding conclusion para

>>>>

In Research Question 1, we used a multiple linear regression (MLR) model to assess how socioeconomic factors affect average life expectancy. The analysis shows that life expectancy is influenced by segregation, uninsured rates, household income, and regional differences, with the Northeast having the highest life expectancy, followed by the Midwest, West, and South. In Research Question 2, we used a logistic regression model to examine how residential segregation, property taxes, and median household income influence school funding adequacy. The results show that region has the greatest impact, with schools in the Northeast and Midwest being significantly more likely to receive adequate funding than those in the South. While residential segregation, property taxes, and household income have statistically significant effects, their influence is minimal compared to regional differences.
